%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% McKenna Jones Resume
% 02/04/2025 <3
%
% Reference:
% https://www.overleaf.com/latex/templates/yet-another-resume-template/gdxwyyqhspsf

\documentclass[]{hieudo-build}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{McKenna Jones}
{\urlstyle{same}
	\faEnvelope \href{mailto:contact@mckennajones.com}{ contact@mckennajones.com}\\
	\faPhone {   (503) 307-5012} \\
	\faGithub \href{https://github.com/mckennajones}{   github/mckennajones}\\
	\faLinkedin \href{https://www.linkedin.com/in/mckenna-jones}{   in/mckenna-jones}}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.25\textwidth} 

\section{Summary} 
Versatile engineer with a passion for delivering highly scalable, customer-focused solutions and fostering collaborative teams. Experienced in cloud-native technologies, distributed systems, and automation, with a unique blend of deep technical expertise and customer-facing experience. Seeking opportunities to drive innovation, lead teams, and deliver meaningful results.\vspace{15pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 

\subsection{Oregon State University}
\descript{BS in Computer Science}
Computer Systems \\
Cum Laude\\

\vspace{15pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
% \subsection{Programming}
\location{Languages}
Go, Python\\
Typescript \& Javascript
\sectionsep

\location{Clouds}
AWS, Azure, GCP
\sectionsep

\location{Tools}
Kubernetes\\
Prometheus, Grafana\\
Terraform\\
Helm\\
Flux
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage} 
\hfill
\begin{minipage}[t]{0.69\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\workplace{MediaKind }{2021 - 2024}\\
\position{Principal Engineer}{Denver, CO}
\vspace{0.9em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed a platform to manage the lifecycle of Kubernetes clusters across Azure, AWS, and GCP, reducing manual intervention.
\item Created Kubernetes operators in Go, revolutionizing the deployment of video workloads to be more robust and scalable.
\item Implemented GitOps models using Flux, enabling automated, consistent deployments across multiple environments.
\item Extensive application monitoring via Prometheus and Grafana, and conducted daily DevOps calls to track down and resolve issues within given SLAs.
\item Development of a greenfield project, rethinking how to deploy and mangage video workloads in a cloud-native way.
\item Took measures to mature cloud footprint, reducing costs, and increasing both reliability and security.

\end{tightemize}

\sectionsep

\workplace{Bitmovin }{2019 - 2021}\\
\position{Solutions Engineer}{Denver, CO}
\begin{tightemize}
\item Served as a technical advisor for existing and prospective customers, ensuring retention and growth of accounts.
\item Developed a framework to perform objective video quality comparisons, resulting in transparent, data-driven discussions with customers.
\item Communicated customer needs to product and engineering teams, enabling a clear path for product innovation.
\item Developed custom video player SDKs focused on dynamic ad insertion, opening new revenue opportunities. 
\item Designated contact for critical customer support issues.
\end{tightemize}

\sectionsep

\workplace{SKIDATA AG }{2017 - 2019}\\
\position{Software Engineer}{Portland, OR}
\begin{tightemize}
\item Transitioned a monolithic .NET application to a microservice architecture, resulting in a more scalable and maintainable system.
\item Participated in a rotating on-call schedule.
\item Managed weekly deployments to AWS infrastructure.
\end{tightemize}

\sectionsep

\workplace{Iovation Inc. }{Summer 2016} \\
\position{QA Engineer Internship }{Portland, OR}
\begin{tightemize}
\item Developed an application to automate the process of creating a QA testing environment, reducing the time to create a new environment from days to minutes.
% \item Use of Hashicorp’s Consul to monitor services
\end{tightemize}


\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{minipage} 

% \section{Projects}
% \runsubsection{OSU Senior Capstone Project: Virtual Reality Outdoor Experience}
% \descript{}
% \location{Top 3 Expo Project as voted by Electrical Engineering and Computer Science industry representatives}
% % \sectionsep
% \vspace{5pt}
% A project sponsored by Intel and Columbia Sportswear. Use of the HTC Vive and the Unity Game Engine to create a virtual reality fishing experience to promote Columbia Sportswear apparel. A yearlong project for the Senior Capstone class at OSU.
% \sectionsep

% \runsubsection{Open Source Contributions}
% \vspace{5pt}

% \location{Elevate - Strava Browser Extension}
% Various merged pull requests related to System Settings that alter site appearance.

% \vspace{5pt}

% \location{Cerebro-Linux-Commands}
% Created a plugin for the productivity tool Cerebro
% in Javascript. Can be found on NPM and GitHub.

\end{document}