%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[1]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications
\usepackage{multicol}
\begin{document}

\header{McKenna}{Jones}{} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
223 NW 15th St.
Corvallis, OR 97330
USA
~
+1 (503) 307 5012
~
\href{mailto:mjones0014@gmail.com}{mjones0014@gmail.com}
\href{https://github.com/mckennajones}{GitHub/mckennajones}
\href{http://facebook.com/mckjns}{facebook/mckjns}
\section{languages}
~
\textbf{Proficient}
C, C++, C\#
~
\textbf{Experience with}
Go
Python
Java
JS, HTML, CSS
SQL
Puppet
\section{tools}
~
\textbf{Proficient with}
Unix, Linux
Windows 7+, OSX
Visual Studio
Git, Github
~
\textbf{Experience with}
Android Studio
Unity Game Engine
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2013-2017}
{Bachelor {\normalfont of Science}}
{Oregon State University}
{\emph{Computer Science} \\ Computer Systems Option - ABET Accreditation \\ 3.63 Engineering GPA}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{relevant work experience}
\begin{entrylist}
%------------------------------------------------
\entry
{2016 - 2017}
{Center for Applied Systems and Software}
{Oregon State University}
{\emph{Student Developer}\hfill \\
Software development for a variety of clients
\begin{itemize}
\item Primarily working on a .NET C\# project for \\
Oregon Department of Transportation
\item Frontend and backend development \\ for MVC web applications
\item Participation in the integration \\ and test cycle of large system releases
\end{itemize}}
\entry
{Sum. 2016}
{Iovation Inc.}
{Portland, OR}
{\emph{QA Engineer Intern}\hfill \\
Summer internship focused on automation
\begin{itemize}
\item Working on project to automate the \\ process of building a QA testing environment
\item Scripting in Bash and Python
\item Participation in an agile development cycle
\item Extensive use of Hashicorp's Consul
\end{itemize}}
\entry
{2015 - 2016}
{Center for Applied Systems and Software}
{Oregon State University}
{\emph{Student Test Engineer}\hfill \\
Testing and debugging of Hewlett \\Packard networking equipment
\begin{itemize}
\item Use of test plans and test suites
\item Bug tracking
\item Manual and automated testing
\end{itemize}}
\end{entrylist}
\section{projects}

\textbf{OSU Senior Capstone Project: Virtual Reality Outdoor Experience}

A project sponsored by Intel and Columbia Sportswear. Use of the HTC Vive and the Unity Game Engine to create a virtual reality fishing experience to promote Columbia Sportswear apparel. A yearlong project for the Senior Capstone class at OSU.

\textbf{Music Discovery App}

An Android application written in Java that informs users of their music listening habits. Code can be found on GitHub.

\textbf{Open Source Contributions}
\begin{itemize}
\item Consul: A service discovery and configuration tool written in Go by Hashicorp. Various bug fixes
\item cerebro-linux-commands: Created a plugin for the productivity cool Cerebro in Javascript. Can be found on NPM and GitHub.
\end{itemize}
\end{document}
